Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-19 scagnostics.Rmd
Filling in example description.

## Data description
The model describes a neutron star merger and contains 6 free parameters, i.e. each neutron star is described by its mass and radius, and a so-called tidal deformability parameter $\Lambda$. A posterior sample containing 2538 points is available @ligoData and can be used to constrain the parameters. For details about the modelling and statistical procedure see @Abbott2018exr.
Show corner plot here, comment on well constrained relation between m1 and m2 ("chirp mass")
For further study we therefore remove m2 from the dataset and use the guided tour working with the remaining 5 dimensions.

Use spline2d index, find relation between 3 parameters, ask Rory for interpretation

>>>>

## Data description
The model describes a neutron star merger and contains 6 free parameters, i.e. each neutron star is described by its mass and radius, and a so-called tidal deformability parameter $\Lambda$. A posterior sample containing 2538 points is available @ligoData and can be used to constrain the parameters. Here we use the "Parametrized-EoS\_nomaxmass\_posterior\_samples.dat" dataset. For details about the modelling and statistical procedure see @Abbott2018exr. A common representation of posterior samples used for interpretatin are so-called "corner plots", i.e. density displays for all 2-d parameter combinations as well as the 1-d profile, highlighting empirically evaluated regions of highest posterior density, which correspond to credibility regions at a given level.
Use Rorys script to make nice version of his corner plot.
Here we generate such a corner plot using the python package "ChainConsumer", highlighting the x and y % CIs. We point out the following features seen from Fig. XX: the combination of the two mass paremters is well constrained (a consequence of how a particular combination, the "chirp mass" enters predictions), other parameters also show patterns of dependence, they are however less pronounces. We highlight the non-linear relation between the radius $R_1$ and $\Lambda$ parameter and the two-pronged structure of the radius $R_1$.
For further study we therefore remove m2 from the dataset. We first look at the distribution in a grand tour display, where we use a scatter plot display combined with alpha blending to study the density distribution in the 5-d parameter space. The grand tour indicates that the data points are found on a curved surface in the five dimensional space. This may stem from a non-linear relation between the parameters, which we will try to uncover using the above developped formalism for new guided tour index functions.

## Using the guided tour
Given the observations from the grand tour display we expect a functional relation between some of the parameters, and we therefore optimise the "splines2d" index function. Note that all parameters are standardised to the range $[0,1]$ before running the optimisation.
Show final view found from the guided tour, give corresponding projection matrix, make corresponding plot from combination of original parameters.
